Capturing Explicit Viewers' Interactions Using Second Screen Devices in iTV Environments

### 2014-06-17 src/paper.tex
Some changes in introduction

% \author{\IEEEauthorblockN{Ricardo E. V. de S. Rosa}
% \IEEEauthorblockA{\\
% Email: ricardoerikson@ufmg.br}
% \and
% \IEEEauthorblockN{Lucas C. Cordeiro and Vicente F. de Lucena Junior}
% \IEEEauthorblockA{Graduate Program in Electrical Engineering \\
% Federal University of Amazonas \\
% Manaus, AM, Brazil\\
% Email: \{lucascordeiro,vicente\}@ufam.edu.br}
% }
\maketitle

@@

TV watching is essentially a social activity, where groups of people with a common interest share the same space and TV set for entertainment or information. After many advances in technologies, for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume. In this scenario, the data generated by the interactions of millions of viewers can provide valuable information for content providers (CPs) to improve their services~\cite{Teixeira2010}.

@@

>>>>

\maketitle

@@

TV watching is essentially a social activity, where groups of people with a common interest share the same space and TV set for entertainment or information~\cite{Masthoff2004}. After many advances in technologies for interactive and digital TV, it is possible to develop high-level applications to enrich the watching experience. Thus, the interaction between viewers and TV became more elaborated than simply change channels and adjust sound volume. In this scenario, the data generated by viewers' interactions can provide valuable information to improve TV services, especially when data comes from millions of viewers~\cite{Teixeira2010}.

@@

As a potential alternative to handle the limitations of the RC for capturing interactions from viewers, the proliferation of personal mobile devices has changed the people behavior towards audiovisual content consumption in interactive TV environments. Nowadays, viewers rarely just sit passively and watch TV. In many situations, they use their personal devices as a secondary screen to perform activities related to TV watching, which end up enriching and immersing the user into the TV experience.
